---
title: "Final Project Code to Submit"
author: "Ethan Hearne"
date: "`r Sys.Date()`"
output: html_document
---

```{r imports, message=FALSE}
library(knitr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(testthat)
load("SpeedDating.rda")
```

###Please forgive my grammar in section titles. R does not like when I use apostrophes, and I needed to remove them to execute the file.

```{r Q1. Are men more likely to say yes to another date than women?}
speedDatingCleanedQ1 <- SpeedDating %>%
  filter(!is.na(DecisionM)) %>%
  filter(!is.na(DecisionF)) %>%
  select(DecisionM, DecisionF)
```

```{r code}
mean_diff <- mean(speedDatingCleanedQ1$DecisionM)- mean(speedDatingCleanedQ1$DecisionF)
print(mean_diff)

nullDist <- replicate(1000, mean(sample(c(0, 1), length(speedDatingCleanedQ1$DecisionM), replace = TRUE)) - 
                        mean(sample(c(0, 1), length(speedDatingCleanedQ1$DecisionF), replace = TRUE)))

p_val <- mean(nullDist >= mean_diff)
print(p_val)
```
```{r null dist boxplot}
 #diff M - F (= .0688, red)"
boxplot(nullDist, 
        main = expression(paste("Null Distribution of ", pi[M], " - ", pi[F], )),
        xlab = expression(paste("Test ", pi[M], " - ", pi[F])),
        horizontal = TRUE)
text(x = mean_diff, 
     y = 1.15, 
     labels = expression(paste('Observed ', pi[M], " - ", pi[F], " =")), 
     pos = 4, 
     col = "red",
     font = 2)
text(x = mean_diff, 
     y = 1.05, 
     labels = paste(round(mean_diff, 4)),
     pos = 4, 
     col = "red",
     font = 2)

abline(v = mean_diff, col = "red")
```



```{r Q2. Which score seems to be the most important for mens Like score?}
speedDatingCleanedQ2 <- na.omit(SpeedDating)
speedDatingCleanedQ2M <- speedDatingCleanedQ2 %>%
  select(LikeM, AgeM, AttractiveM, SincereM, IntelligentM, FunM, AmbitiousM, SharedInterestsM)
```

```{r test which is the best individual predictor by comparing r-square of each predictor.}
predictors = colnames(speedDatingCleanedQ2M)[-1] #This is because LikeM is the first column in the df.
rsq_dict <- setNames(numeric(length(predictors)), predictors)

Age_model = lm(speedDatingCleanedQ2M$LikeM ~ speedDatingCleanedQ2M$AgeM)
Age_model_summary = summary(Age_model)
Age_rsq = Age_model_summary$r.squared
rsq_dict$AgeM <- Age_rsq

Attractive_model = lm(speedDatingCleanedQ2M$LikeM ~ speedDatingCleanedQ2M$AttractiveM)
Attractive_model_summary = summary(Attractive_model)
Attractive_rsq = Attractive_model_summary$r.squared
rsq_dict$AttractiveM <- Attractive_rsq

Sincere_model = lm(speedDatingCleanedQ2M$LikeM ~ speedDatingCleanedQ2M$SincereM)
Sincere_model_summary = summary(Sincere_model)
Sincere_rsq = Sincere_model_summary$r.squared
rsq_dict$SincereM <- Sincere_rsq

Intelligent_model = lm(speedDatingCleanedQ2M$LikeM ~ speedDatingCleanedQ2M$IntelligentM)
Intelligent_model_summary = summary(Intelligent_model)
Intelligent_rsq = Intelligent_model_summary$r.squared
rsq_dict$IntelligentM <- Intelligent_rsq

Fun_model = lm(speedDatingCleanedQ2M$LikeM ~ speedDatingCleanedQ2M$FunM)
Fun_model_summary = summary(Fun_model)
Fun_rsq = Fun_model_summary$r.squared
rsq_dict$FunM <- Fun_rsq

Ambitious_model = lm(speedDatingCleanedQ2M$LikeM ~ speedDatingCleanedQ2M$AmbitiousM)
Ambitious_model_summary = summary(Ambitious_model)
Ambitious_rsq = Ambitious_model_summary$r.squared
rsq_dict$AmbitiousM <- Ambitious_rsq

SharedInterests_model = lm(speedDatingCleanedQ2M$LikeM ~ speedDatingCleanedQ2M$SharedInterestsM)
SharedInterests_model_summary = summary(SharedInterests_model)
SharedInterests_rsq = SharedInterests_model_summary$r.squared
rsq_dict$SharedInterestsM <- SharedInterests_rsq

print(rsq_dict)
```
By comparing the r squared values for each variable's ability to predict how much the man likes the woman, we can conclude that the single best predictor is how attractive the man finds the woman, with an r squared value of .5171.

```{r Q3. Do larger age gaps affect if either a man or a woman view each other as attractive?}
speedDatingCleanedQ3 <- SpeedDating %>%
  filter(!is.na(AgeM)) %>%
  filter(!is.na(AgeF)) %>%
  filter(!is.na(AttractiveM)) %>%
  filter(!is.na(AttractiveF)) %>%
  mutate(ageDiffM = AgeM - AgeF) %>%
  mutate(ageDiffF = AgeF - AgeM) %>%
  select(ageDiffM, ageDiffF, AttractiveM, AttractiveF)
```

```{r relevant plots and Sample Correlation}
plot(speedDatingCleanedQ3$ageDiffM, speedDatingCleanedQ3$AttractiveM, xlab = "Age Difference Between Men and Women", ylab = "How Attractive do Men Rate Women", main = "Age Gap between Men and Women vs Rated Attractiveness")

CorM <- cor(speedDatingCleanedQ3$ageDiffM, speedDatingCleanedQ3$AttractiveM)

plot(speedDatingCleanedQ3$ageDiffF, speedDatingCleanedQ3$AttractiveF, xlab = "Age Difference Between Women and Men", ylab = "How Attractive do Women Rate Men", main = "Age Gap between Women and Men vs Rated Attractiveness")

CorF <- cor(speedDatingCleanedQ3$ageDiffF, speedDatingCleanedQ3$AttractiveF)

print(CorM)
print(CorF)
```
```{r test code for Males}
shuffleM <- function(male){
  shuffledM <- male %>%
    mutate(shuffled_ageDiffM = sample(ageDiffM, length(ageDiffM), replace=FALSE))
  
  return(cor(shuffledM$shuffled_ageDiffM, shuffledM$AttractiveM, method = "pearson"))
}

nulldistM <- replicate(1000, shuffleM(speedDatingCleanedQ3))

boxplot(nulldistM, horizontal = TRUE, main = "Null Dist of Correlations Between M-F Age Gaps and Rated Attractiveness", xlab = "Test Correlation")
abline(v = CorM, col = "red")
text(x = 0.12, y = 1.15, labels = paste("Observed CorM = "), pos = 3, col = "red")
text(x = 0.12, y = 1.05, labels = paste(round(CorM, 4)), pos = 3, col = "red")


```
```{r histogram for men}
hist(nulldistM,
     main = "Null Dist of Correlations Between M-F Age Gaps and Rated Attractiveness",
     xlab = paste("Test Correlation"),
     col = "lightgray",
     border = "black")

abline(v = CorM, col = "red", lwd = 2)
text(x = 0.16, y = 250, labels = paste("Observed CorM = ", round(CorM, 4)), pos = 3, col = "red")

```

```{r test code for Women}
shuffleF <- function(female){
  shuffledF <- female %>%
    mutate(shuffled_ageDiffF = sample(ageDiffF, length(ageDiffF), replace=FALSE))
  
  return(cor(shuffledF$shuffled_ageDiffF, shuffledF$AttractiveF, method = "pearson"))
}

nulldistF <- replicate(1000, shuffleF(speedDatingCleanedQ3))

boxplot(nulldistF, horizontal = TRUE, main = "Null Dist of Correlations Between F-M Age Gaps and Rated Attractiveness", xlab = "Test Correlation = .0670, red")
abline(v = CorF, col = "red")
text(x = 0.14, y = 1.15, labels = paste("Observed CorF = ", round(CorF, 4)), pos = 3, col = "red")

```
```{r added hist for women}
hist(nulldistF,
     main = "Null Dist of Correlations Between F-M Age Gaps and Rated Attractiveness",
     xlab = "Test Correlation",
     col = "lightgray",
     border = "black")


abline(v = CorF, col = "red", lwd = 2)
text(x = 0.13, y = 250, labels = paste("Observed CorF = "), pos = 3, col = "red")
text(x = 0.13, y = 220, labels = paste(round(CorF, 4)), pos = 3, col = "red")

```

```{r obtaining p values}
p_valM <- mean(CorM <= nulldistM)

p_valF <- mean(CorF <= nulldistF)

print(p_valM)
print(p_valF)
```
Given the p-values that we obtained for men and women respectively, we fail to reject the null hypothesis at a significance level of a = .05.



```{r Q4. Do people find people they view as attractive to be more fun.}
speedDatingCleanedQ4 <- SpeedDating %>%
  filter(!is.na(AttractiveM)) %>%
  filter(!is.na(AttractiveF)) %>%
  filter(!is.na(FunM)) %>%
  filter(!is.na(FunF)) %>%
  select(AttractiveM, AttractiveF, FunM, FunF)
```

```{r plotting mens view of womens attractiveness vs fun and their correlation.}
plot(jitter(speedDatingCleanedQ4$AttractiveM), jitter(speedDatingCleanedQ4$FunM), xlab = "How Attractive Do Men View Women As? (1-10)", ylab = "How Fun Do Men View Women As? (1-10)", main = "Men's Rating of Women's Attractiveness vs How Fun They Are with")

abline(lm(speedDatingCleanedQ4$FunM ~ speedDatingCleanedQ4$AttractiveM), col = "red")

CorM <- cor(speedDatingCleanedQ4$AttractiveM, speedDatingCleanedQ4$FunM, method = "pearson")
print(CorM)
```
There appears to be a moderate positive correlation between how men view women as attractive vs how fun they view women.
To test this, we run a shuffle test to determine the significance of this correlation.


```{r Male shuffle test}
shuffleM <- function(male){
  shuffledM <- male %>%
    mutate(shuffled_AttractiveM = sample(AttractiveM, length(AttractiveM), replace=FALSE))
  
  return(cor(shuffledM$shuffled_AttractiveM, shuffledM$FunM, method = "pearson"))
}


nulldistM <- replicate(1000, shuffleM(speedDatingCleanedQ4))

boxplot(nulldistM, main = "Null Dist of How Men Rate Women as Attractive vs Fun", horizontal = TRUE, ylim = c(-.25, .25), xlab = "Test Correlation")
abline(v = CorM, col = "red")
text(x = 0.16, y = 1.15, labels = paste("Observed CorM = ", round(CorM, 4)), pos = 3, col = "red")


p_valM <- mean(CorM <= nulldistM)
print(p_valM)
```
We reject the null hypothesis that there is no correlation between how men perceive women as attractive vs how they percieve them as fun at a = .05, because the p value is 0.

```{r testing the shuffle function. It is the same function for both Women and Men, just with different names.}
#All the functions with "shuffle" and then a letter after "shuffle" are the same
# thing but with a different column being shuffled and used to check the 
# respective correlations. For all intents and purposes, it is just one function
# with name changes for different use cases. Uncomment lines as needed for
# testing purposes.
shuffleM <- function(male){
  shuffledM <- male %>%
    mutate(shuffled_AttractiveM = sample(AttractiveM, length(AttractiveM), replace=FALSE))
  
  return(cor(shuffledM$shuffled_AttractiveM, shuffledM$FunM, method = "pearson"))
}

#Test 1: inputting a dataframe to shuffleM that contains no "AttractiveM" column. This should raise an error.
#test1 <- speedDatingCleanedQ4 %>%
#  select(FunM, FunF, AttractiveF)
#shuffleM(test1$AttractiveM)

#Test 2: inputting a dataframe into shuffleM, where "AttractiveM" containes non numeric values. This should raise an error.
#test2 <- speedDatingCleanedQ4 %>%
#  mutate(AttractiveM = NA)
#shuffleM(test2$AttractiveM)

#Test 3: replace "AttractiveM" with "FunM". this should raise an error
#test3_output <- shuffleM(speedDatingCleanedQ4$FunM)
```


```{r plotting womens view of mens attractiveness vs fun and their correlation.}
plot(jitter(speedDatingCleanedQ4$AttractiveF), jitter(speedDatingCleanedQ4$FunF), xlab = "How Attractive Do Women View Men As? (1-10)", ylab = "How Fun Do Women View Men As? (1-10)", main = "Women's Rating of Men's Attractiveness vs How Fun They Are")
abline(lm(speedDatingCleanedQ4$FunF ~ speedDatingCleanedQ4$AttractiveF), col = "red")

CorF <- cor(speedDatingCleanedQ4$AttractiveF, speedDatingCleanedQ4$FunF, method = "pearson")
print(CorF)
```
There appears to be a moderate positive correlation between how Women view Men as attractive vs how fun they view men.
To test this, we run a shuffle test to determine the significance of this correlation.

```{r Women shuffle test}
shuffleF <- function(female){
  shuffledF <- female %>%
    mutate(shuffled_AttractiveF = sample(AttractiveF, length(AttractiveF), replace=FALSE))
  
  return(cor(shuffledF$shuffled_AttractiveF, shuffledF$FunF, method = "pearson"))
}


nulldistF <- replicate(1000, shuffleF(speedDatingCleanedQ4))

boxplot(nulldistF, main = "Null Dist of How Women Percieve Men as Attractive vs Fun", horizontal = TRUE, ylim = c(-.25, .25), xlab = "Test Correlation")
abline(v = CorF, col = "red")
text(x = 0.16, y = 1.15, labels = paste("Observed CorF = ", round(CorF, 4)), pos = 3, col = "red")

p_valF <- mean(CorF <= nulldistF)
print(p_valF)
```

We reject the null hypothesis that there is no correlation between how women percieve men as attractive vs how they percieve them as fun at a = .05, because the p value is 0.

```{r linear regression for both m and f with summaries}
modelM <- lm(speedDatingCleanedQ4$FunM ~ speedDatingCleanedQ4$AttractiveM)
summary(modelM)

modelF <- lm(speedDatingCleanedQ4$FunF ~ speedDatingCleanedQ4$AttractiveF)
summary(modelF)
```

